---
title: "Data_Cleaning"
output: html_document
date: "2025-01-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Mexico Public Debt Data Cleaning 
## Fuente: Secretaría de Hacienda y Crédito Público (SHCP) - Registro Público Único
## Link: https://www.disciplinafinanciera.hacienda.gob.mx/es/DISCIPLINA_FINANCIERA/Registro_Publico_Unico
## Authors Iván Zamorano, Rafael Ch

# Libraries

```{r chunk1}
#You can also use the pacman library if you want to read the rest of libraries with one command.
library(readxl)
library(dplyr)
library(magrittr)
library(openxlsx)
```


# Get the data (link in the source, XLSX file)
# We will ignore the first row since it only contains the tittle "FINANCIAMIENTOS Y OBLIGACIONES INSCRITOS EN EL REGISTRO PÚBLICO ÚNICO 1/".
# We will ignore the second row since it only contains blank spaces.


```{r get data , echo=FALSE}
file_path <- "registro_deuda (1).xlsx"
registro_deuda_1<- read.xlsx(file_path, startRow = 2) %>%
  slice(-1)
```

#Data Glimpse
```{r get data , echo=FALSE}
View(registro_deuda_1)
```

#Data Structure - Explanation:

* For Amount we used "Monto Original Contratado"
* For Maturirities we used "Fecha de Vencimiento" (note that there are some values)
* Other important dates are "Contract date", "Inscription Date" and "Days agreed for paying", we can add the "Contract date" or the "Inscription date" plus the "Days agreed for paying".
* For rates we used "Tasa Efectiva" but we can also use the "Tasa de interés", "Sobretasa", "Porcentaje Afectado" and "Tasa garantizada". 


# Filter by municipalities 

```{r municipalities , echo=FALSE}
# Create a new data frame with rows containing "municipio"
registro_deuda_municipal_1 <- registro_deuda_1_[grepl("municipio", registro_deuda_1_$DEUDOR.U.OBLIGADO.2, ignore.case = TRUE), ]
# Create a new data frame with rows containing "municipal"

registro_deuda_municipal_2 <- registro_deuda_1_[grepl("municipal", registro_deuda_1_$DEUDOR.U.OBLIGADO.2, ignore.case = TRUE), ]
registro_deuda_municipal <- rbind(registro_deuda_municipal_1, registro_deuda_municipal_2)
registro_deuda_municipal <- registro_deuda_municipal[, c("MONTO.ORIGINAL.CONTRATADO.7/", "DEUDOR.U.OBLIGADO.2/", "FECHA.DE.VENCIMIENTO.27/", "TASA.EFECTIVA.13/")]
write.xlsx(registro_deuda_municipal, file = "registro_deuda_municipal.xlsx")
```


# Filter by states 
```{r municipalities , echo=FALSE}

# Create a new data frame with rows containing "Estado"
registro_deuda_estatal_1 <- registro_deuda_1_[grepl("Estado", registro_deuda_1_$DEUDOR.U.OBLIGADO.2, ignore.case = TRUE),]
# Create a new data frame with rows containing "Estatal"
registro_deuda_estatal_2 <- registro_deuda_1_[grepl("Estatal", registro_deuda_1_$DEUDOR.U.OBLIGADO.2, ignore.case = TRUE),]
registro_deuda_estatal <- rbind(registro_deuda_estatal_1, registro_deuda_estatal_2)
registro_deuda_estatal <- registro_deuda_estatal[, c("MONTO.ORIGINAL.CONTRATADO.7/", "DEUDOR.U.OBLIGADO.2/", "FECHA.DE.VENCIMIENTO.27/", "TASA.EFECTIVA.13/")]
write.xlsx(registro_deuda_estatal, file = "resgistro_deuda_estatal.xlsx")

```



