---
title: "Data_Cleaning"
output: html_document
date: "2025-01-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Mexico Public Debt Data Cleaning 
## Fuente: Secretaría de Hacienda y Crédito Público (SHCP) - Registro Público Único
## Link: https://www.disciplinafinanciera.hacienda.gob.mx/es/DISCIPLINA_FINANCIERA/Registro_Publico_Unico
## Authors Iván Zamorano, Rafael Ch

# Libraries

```{r chunk1}
#You can also use the pacman library if you want to read the rest of libraries with one command.
library(readxl)
library(dplyr)
library(magrittr)
library(openxlsx)
```


# Get the data (link in the source, XLSX file)
# We will ignore the first row since it only contains the tittle "FINANCIAMIENTOS Y OBLIGACIONES INSCRITOS EN EL REGISTRO PÚBLICO ÚNICO 1/".
# We will ignore the second row since it only contains blank spaces.
# We will remove the last 4 rows because they contain metadata that's not useful. 
# Renaming the column from "Saldo.total" to "2Q2019". 
# Renaming the column from "Entidad.Federativa" to "EntidadFed". 
# Data from: 20192Q - 20233Q



```{r get data 2024 , echo=FALSE}
############################ 2024 ############################    

Q12024 <- "Quarterly/02_04_1_trim_2024.xlsx"
Q1_2024 <- read.xlsx(Q12024, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("1Q2024" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.Federativa")  %>% 
  select("EntidadFed", "1Q2024")  # Select only the desired column
Q1_2024$id <- seq_len(nrow(Q1_2024))
print(Q1_2024rows <- nrow(Q1_2024))


Q22024 <- "Quarterly/02_04_2_trim_2023.xlsx"
Q2_2024 <- read.xlsx(Q22024, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("2Q2024" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.Federativa")  %>% 
  select("EntidadFed", "2Q2024")  # Select only the desired column
Q2_2024$id <- seq_len(nrow(Q2_2024))
print(Q2_2024rows <- nrow(Q2_2024))


Q32024 <- "Quarterly/02_04_3_trim_2023.xlsx"
Q3_2024 <- read.xlsx(Q32024, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("3Q2024" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.Federativa")  %>% 
  select("EntidadFed", "3Q2024")  # Select only the desired column
Q3_2024$id <- seq_len(nrow(Q3_2024))
print(Q3_2024rows <- nrow(Q3_2024))

merged_data_2024 <- Q1_2024 %>%
  left_join(Q2_2024, by = "id") %>%
  left_join(Q3_2024, by = "id") 

merged_data_2024  <- merged_data_2024 %>%
  select(-EntidadFed.y, -EntidadFed, -EntidadFed.x)

```



```{r get data 2023 , echo=FALSE}
############################ 2023 ############################    

Q12023 <- "Quarterly/02_04_1_trim_2023.xlsx"
Q1_2023 <- read.xlsx(Q12023, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("1Q2023" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.federativa")  %>% 
  select("EntidadFed", "1Q2023")  # Select only the desired column
Q1_2023$id <- seq_len(nrow(Q1_2023))
print(Q1_2023rows <- nrow(Q1_2023))


Q22023 <- "Quarterly/02_04_2_trim_2023.xlsx"
Q2_2023 <- read.xlsx(Q22023, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("2Q2023" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.Federativa")  %>% 
  select("EntidadFed", "2Q2023")  # Select only the desired column
Q2_2023$id <- seq_len(nrow(Q2_2023))
print(Q2_2023rows <- nrow(Q2_2023))


Q32023 <- "Quarterly/02_04_3_trim_2023.xlsx"
Q3_2023 <- read.xlsx(Q32023, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("3Q2023" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.Federativa")  %>% 
  select("EntidadFed", "3Q2023")  # Select only the desired column
Q3_2023$id <- seq_len(nrow(Q3_2023))
print(Q3_2023rows <- nrow(Q3_2023))


Q42023 <- "Quarterly/02_04_4_trim_2023.xlsx"
Q4_2023 <- read.xlsx(Q42023, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("4Q2023" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.Federativa")  %>% 
  select("EntidadFed", "4Q2023")  # Select only the desired column
Q4_2023$id <- seq_len(nrow(Q4_2023))
print(Q4_2023rows <- nrow(Q4_2023))

merged_data_2023 <- Q1_2023 %>%
  left_join(Q2_2023, by = "id") %>%
  left_join(Q3_2023, by = "id") %>%
  left_join(Q4_2023, by = "id")

merged_data_2023  <- merged_data_2023 %>%
  select(-EntidadFed.y, -EntidadFed.x.x, -EntidadFed.y.y)

```

```{r get data 2022 , echo=FALSE}
############################ 2022 ############################    

Q12022 <- "Quarterly/02_04_1_trim_2022.xlsx"
Q1_2022 <- read.xlsx(Q12022, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("1Q2022" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.federativa")  %>% 
  select("EntidadFed", "1Q2022")  # Select only the desired column
Q1_2022$id <- seq_len(nrow(Q1_2022))
print(Q1_2022rows <- nrow(Q1_2022))


Q22022 <- "Quarterly/02_04_2_trim_2022.xlsx"
Q2_2022 <- read.xlsx(Q22022, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("2Q2022" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.federativa")  %>% 
  select("EntidadFed", "2Q2022")  # Select only the desired column
Q2_2022$id <- seq_len(nrow(Q2_2022))
print(Q2_2022rows <- nrow(Q2_2022))


Q32022 <- "Quarterly/02_04_3_trim_2022.xlsx"
Q3_2022 <- read.xlsx(Q32022, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("3Q2022" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.federativa")  %>% 
  select("EntidadFed", "3Q2022")  # Select only the desired column
Q3_2022$id <- seq_len(nrow(Q3_2022))
print(Q3_2022rows <- nrow(Q3_2022))


Q42022 <- "Quarterly/02_04_4_trim_2022 (1).xlsx"
Q4_2022 <- read.xlsx(Q42022, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("4Q2022" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.federativa")  %>% 
  select("EntidadFed", "4Q2022")  # Select only the desired column
Q4_2022$id <- seq_len(nrow(Q4_2022))
print(Q4_2022rows <- nrow(Q4_2022))

merged_data_2022 <- Q1_2022 %>%
  left_join(Q2_2022, by = "id") %>%
  left_join(Q3_2022, by = "id") %>%
  left_join(Q4_2022, by = "id")

merged_data_2022  <- merged_data_2022 %>%
  select(-EntidadFed.y, -EntidadFed.x.x, -EntidadFed.y.y)

```


```{r get data 2021 , echo=FALSE}
############################ 2021 ############################    

Q1_2021 <- read_excel("Quarterly/02_04_1_trim_2021.xls", range = "A4:F2487") %>%
  slice(1:(n() - 4)) %>% 
  rename("1Q2021" = "Saldo total") %>%
  rename("EntidadFed" = "Entidad federativa")  %>% 
  select("EntidadFed", "1Q2021")

Q1_2021$id <- seq_len(nrow(Q1_2021))
print(Q1_2021rows <- nrow(Q1_2021))


Q2_2021 <- read_excel("Quarterly/02_04_2_trim_2021.xls", range = "A4:F2487") %>%
  slice(1:(n() - 4)) %>% 
  rename("2Q2021" = "Saldo total") %>%
  rename("EntidadFed" = "Entidad federativa")  %>% 
  select("EntidadFed", "2Q2021")

Q2_2021$id <- seq_len(nrow(Q2_2021))
print(Q2_2021rows <- nrow(Q2_2021))


Q32021 <- "Quarterly/02_04_3_trim_2021.xlsx"
Q3_2021 <- read.xlsx(Q32021, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("3Q2021" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.federativa")  %>% 
  select("EntidadFed", "3Q2021")  # Select only the desired column

Q3_2021$id <- seq_len(nrow(Q3_2021))
print(Q3_2021rows <- nrow(Q3_2021))

Q42021 <- "Quarterly/02_04_4_trim_2021.xlsx"
Q4_2021 <- read.xlsx(Q42021, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("4Q2021" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.federativa")  %>% 
  select("EntidadFed", "4Q2021")  # Select only the desired column

Q4_2021$id <- seq_len(nrow(Q4_2021))
print(Q4_2021rows <- nrow(Q4_2021))

merged_data_2021 <- Q1_2021 %>%
  left_join(Q2_2021, by = "id") %>%
  left_join(Q3_2021, by = "id") %>%
  left_join(Q4_2021, by = "id")

merged_data_2021  <- merged_data_2021 %>%
  select(-EntidadFed.y, -EntidadFed.x.x, -EntidadFed.y.y)

```

```{r get data 2020 , echo=FALSE}

############################ 2020 ############################    

Q1_2020 <- read_excel("Quarterly/02_04_1_trim_2020.xls", range = "A4:F2487") %>%
  slice(1:(n() - 4)) %>% 
  rename("1Q2020" = "Saldo total") %>%
  rename("EntidadFed" = "Entidad federativa")  %>% 
  select("EntidadFed", "1Q2020")

Q1_2020$id <- seq_len(nrow(Q1_2020))
print(Q1_2020rows <- nrow(Q1_2020))



Q2_2020 <- read_excel("Quarterly/02_04_2_trim_2020.xls", range = "A4:F2487") %>%
  slice(1:(n() - 4)) %>% 
  rename("2Q2020" = "Saldo total") %>%
  rename("EntidadFed" = "Entidad federativa")  %>% 
  select("EntidadFed", "2Q2020")

Q2_2020$id <- seq_len(nrow(Q2_2020))
print(Q2_2020rows <- nrow(Q2_2020))



Q3_2020 <- read_excel("Quarterly/02_04_3_trim_2020.xls", range = "A4:F2487") %>%
  slice(1:(n() - 4)) %>% 
  rename("3Q2020" = "Saldo total") %>%
  rename("EntidadFed" = "Entidad federativa")  %>% 
  select("EntidadFed", "3Q2020")

Q3_2020$id <- seq_len(nrow(Q3_2020))
print(Q3_2020rows <- nrow(Q3_2020))



Q4_2020 <- read_excel("Quarterly/02_04_4_trim_2020.xls", range = "A4:F2487") %>%
  slice(1:(n() - 4)) %>% 
  rename("4Q2020" = "Saldo total") %>%
  rename("EntidadFed" = "Entidad federativa")  %>% 
  select("EntidadFed", "4Q2020")
print(Q3_2020rows <- nrow(Q4_2020))

Q4_2020$id <- seq_len(nrow(Q4_2020))
print(Q4_2020rows <- nrow(Q4_2020))

merged_data_2020 <- Q1_2020 %>%
  left_join(Q2_2020, by = "id") %>%
  left_join(Q3_2020, by = "id") %>%
  left_join(Q4_2020, by = "id")

merged_data_2020  <- merged_data_2020 %>%
  select(-EntidadFed.y, -EntidadFed.x.x, -EntidadFed.y.y)
```


```{r get data 2019 , echo=FALSE}
############################ 2019 ############################    

Q22019 <- "Quarterly/02_04_2_trim_2019.xlsx"
Q2_2019 <- read.xlsx(Q22019, startRow = 4) %>%
  slice(1:(n() - 4)) %>% 
  rename("2Q2019" = "Saldo.total")  %>% 
  rename("EntidadFed" = "Entidad.federativa")  %>% 
  select("EntidadFed", "2Q2019")  # Select only the desired columns

Q2_2019$id <- seq_len(nrow(Q2_2019))
print(Q2_2019rows <- nrow(Q2_2019))



Q3_2019 <- read_excel("Quarterly/02_04_3_trim_2019.xls", range = "A4:F2487") %>%
  slice(1:(n() - 4)) %>% 
  rename("3Q2019" = "Saldo total") %>%
  rename("EntidadFed" = "Entidad federativa")  %>% 
  select("EntidadFed", "3Q2019")
Q3_2019$id <- seq_len(nrow(Q3_2019))
print(Q3_2019rows <- nrow(Q3_2019))


Q4_2019 <- read_excel("Quarterly/02_04_4_trim_2019.xls", range = "A4:F2487") %>%
  slice(1:(n() - 4)) %>% 
  rename("4Q2019" = "Saldo total") %>%
  rename("EntidadFed" = "Entidad federativa")  %>% 
  select("EntidadFed", "4Q2019")
Q4_2019$id <- seq_len(nrow(Q4_2019))
print(Q4_20219rows <- nrow(Q4_2019))



merged_data_2019 <- Q2_2019 %>%
  left_join(Q3_2019, by = "id") %>%
  left_join(Q4_2019, by = "id")

merged_data_2019  <- merged_data_2019 %>%
  select(-EntidadFed.y, -EntidadFed.x)


merged_data_2019_2020 <- merged_data_2019 %>%
  left_join(merged_data_2020, by = "id")

merged_data_2019_2020   <- merged_data_2019_2020 %>%
  select(-EntidadFed.x, -id)


```


```{r get data 2018 , echo=FALSE}
############################ 2018 ############################    

library(tidyr)

Q12018 <- read_excel("Quarterly/02_04_1_trim_2018.xlsx", skip = 1)

colnames(Q12018)[1] <- "Entidad.federativa"
colnames(Q12018)[2] <- "Saldo.total"

Q1_2018 <- Q12018 %>%
  slice(1:(n() - 4)) %>%                # Remove the last 4 rows
  rename(`1Q2018` = `Saldo.total`) %>%  # Rename "Saldo.total" to "1Q2018"
  rename(EntidadFed = `Entidad.federativa`) %>% # Rename "Entidad.federativa" to "EntidadFed"
  select(EntidadFed, `1Q2018`) %>%      # Select only the desired columns
  drop_na()                             # Remove rows where any column has NA
                          # Remove rows where any column has NA
Q1_2018$id <- seq_len(nrow(Q1_2018))


Q22018 <- read_excel("Quarterly/02_04_2_trim_2018.xlsx", skip = 1)

colnames(Q22018)[1] <- "Entidad.federativa"
colnames(Q22018)[2] <- "Saldo.total"

Q2_2018 <- Q22018 %>%
  slice(1:(n() - 4)) %>%                # Remove the last 4 rows
  rename(`2Q2018` = `Saldo.total`) %>%  # Rename "Saldo.total" to "1Q2018"
  rename(EntidadFed = `Entidad.federativa`) %>% # Rename "Entidad.federativa" to "EntidadFed"
  select(EntidadFed, `2Q2018`) %>%      # Select only the desired columns
  drop_na()                             # Remove rows where any column has NA
                          # Remove rows where any column has NA
Q2_2018$id <- seq_len(nrow(Q2_2018))

Q32018 <- read_excel("Quarterly/02_04_3_trim_2018.xlsx", skip = 1)

colnames(Q32018)[1] <- "Entidad.federativa"
colnames(Q32018)[2] <- "Saldo.total"

Q3_2018 <- Q32018 %>%
  slice(1:(n() - 4)) %>%                # Remove the last 4 rows
  rename(`3Q2018` = `Saldo.total`) %>%  # Rename "Saldo.total" to "1Q2018"
  rename(EntidadFed = `Entidad.federativa`) %>% # Rename "Entidad.federativa" to "EntidadFed"
  select(EntidadFed, `3Q2018`) %>%      # Select only the desired columns
  drop_na()                             # Remove rows where any column has NA
                          # Remove rows where any column has NA

Q3_2018$id <- seq_len(nrow(Q3_2018))


Q42018 <- read_excel("Quarterly/02_04_4_trim_2018.xlsx", skip = 1)

colnames(Q42018)[1] <- "Entidad.federativa"
colnames(Q42018)[2] <- "Saldo.total"

Q4_2018 <- Q42018 %>%
  slice(1:(n() - 4)) %>%                # Remove the last 4 rows
  rename(`4Q2018` = `Saldo.total`) %>%  # Rename "Saldo.total" to "1Q2018"
  rename(EntidadFed = `Entidad.federativa`) %>% # Rename "Entidad.federativa" to "EntidadFed"
  select(EntidadFed, `4Q2018`) %>%      # Select only the desired columns
  drop_na()                             # Remove rows where any column has NA
                          # Remove rows where any column has NA

Q4_2018$id <- seq_len(nrow(Q4_2018))

merged_data_2018 <- Q1_2018 %>%
  left_join(Q2_2018, by = "id") %>%
  left_join(Q3_2018, by = "id") %>%
  left_join(Q4_2018, by = "id")

merged_data_2018  <- merged_data_2018 %>%
  select(-EntidadFed.y, -EntidadFed.x.x, -EntidadFed.y.y)

```


```{r get data 2017 , echo=FALSE}
############################ 2017 ############################    

library(tidyr)

Q12017 <- read_excel("Quarterly/02_04_1_trim_2017.xlsx", skip = 1)
colnames(Q12017)[1] <- "Entidad.federativa"
colnames(Q12017)[2] <- "Saldo.total"

Q1_2017 <- Q12017 %>%
  slice(1:(n() - 4)) %>%                # Remove the last 4 rows
  rename(`1Q2017` = `Saldo.total`) %>%  # Rename "Saldo.total" to "1Q2018"
  rename(EntidadFed = `Entidad.federativa`) %>% # Rename "Entidad.federativa" to "EntidadFed"
  select(EntidadFed, `1Q2017`) %>%      # Select only the desired columns
  drop_na()                             # Remove rows where any column has NA
                          # Remove rows where any column has NA
Q1_2017$id <- seq_len(nrow(Q1_2017))


Q22017 <- read_excel("Quarterly/02_04_2_trim_2017.xlsx", skip = 1)
colnames(Q22017)[1] <- "Entidad.federativa"
colnames(Q22017)[2] <- "Saldo.total"

Q2_2017 <- Q22017 %>%
  slice(1:(n() - 4)) %>%                # Remove the last 4 rows
  rename(`2Q2017` = `Saldo.total`) %>%  # Rename "Saldo.total" to "1Q2018"
  rename(EntidadFed = `Entidad.federativa`) %>% # Rename "Entidad.federativa" to "EntidadFed"
  select(EntidadFed, `2Q2017`) %>%      # Select only the desired columns
  drop_na()                             # Remove rows where any column has NA
                          # Remove rows where any column has NA
Q2_2017$id <- seq_len(nrow(Q2_2017))


Q32017 <- read_excel("Quarterly/02_04_3_trim_2017.xlsx", skip = 1)
colnames(Q32017)[1] <- "Entidad.federativa"
colnames(Q32017)[2] <- "Saldo.total"

Q3_2017 <- Q32017 %>%
  slice(1:(n() - 4)) %>%                # Remove the last 4 rows
  rename(`3Q2017` = `Saldo.total`) %>%  # Rename "Saldo.total" to "1Q2018"
  rename(EntidadFed = `Entidad.federativa`) %>% # Rename "Entidad.federativa" to "EntidadFed"
  select(EntidadFed, `3Q2017`) %>%      # Select only the desired columns
  drop_na()                             # Remove rows where any column has NA
                          # Remove rows where any column has NA
Q3_2017$id <- seq_len(nrow(Q3_2017))


Q42017 <- read_excel("Quarterly/02_04_4_trim_2017.xlsx", skip = 1)
colnames(Q42017)[1] <- "Entidad.federativa"
colnames(Q42017)[2] <- "Saldo.total"

Q4_2017 <- Q42017 %>%
  slice(1:(n() - 4)) %>%                # Remove the last 4 rows
  rename(`4Q2017` = `Saldo.total`) %>%  # Rename "Saldo.total" to "1Q2018"
  rename(EntidadFed = `Entidad.federativa`) %>% # Rename "Entidad.federativa" to "EntidadFed"
  select(EntidadFed, `4Q2017`) %>%      # Select only the desired columns
  drop_na()                             # Remove rows where any column has NA
                          # Remove rows where any column has NA
Q4_2017$id <- seq_len(nrow(Q4_2017))

merged_data_2017 <- Q1_2017 %>%
  left_join(Q2_2017, by = "id") %>%
  left_join(Q3_2017, by = "id") %>%
  left_join(Q4_2017, by = "id")

merged_data_2017  <- merged_data_2017 %>%
  select(-EntidadFed.y, -EntidadFed.x.x, -EntidadFed.y.y)

```





```{r merge data years  , echo=FALSE}

merged_data_2019_2020 <- merged_data_2019 %>%
  left_join(merged_data_2020, by = "id")

merged_data_2019_2020 <- merged_data_2019 %>%
  left_join(merged_data_2020, by = "id")

merged_data_2019_2020_2021 <- merged_data_2019_2020 %>%
  left_join(merged_data_2021, by = "id")

merged_data_2019_2020_2021_2022 <- merged_data_2019_2020_2021 %>%
  left_join(merged_data_2022, by = "id")

merged_data_2019_2020_2021_2022_2023 <- merged_data_2019_2020_2021_2022 %>%
  left_join(merged_data_2023, by = "id")

merged_data_2019_2020_2021_2022_2023_2024 <- merged_data_2019_2020_2021_2022_2023 %>%
  left_join(merged_data_2024, by = "id")

merged_data_2018_2019_2020_2021_2022_2023_2024 <- merged_data_2019_2020_2021_2022_2023 %>%
  left_join(merged_data_2018, by = "id")

merged_data_2017_2018_2019_2020_2021_2022_2023_2024 <- merged_data_2018_2019_2020_2021_2022_2023_2024 %>%
  left_join(merged_data_2017, by = "id")


merged_data_2017_2018_2019_2020_2021_2022_2023_2024 <- merged_data_2017_2018_2019_2020_2021_2022_2023_2024 %>%
  select(-EntidadFed.x.x, -EntidadFed.x.y, -EntidadFed.x.x.x, -EntidadFed.x.x.x.x, -EntidadFed.x.y.y, -EntidadFed.x.y.y.y,-id)



```



#Data Glimpse
```{r get data , echo=FALSE}
View(Q2_2019)
```

#Data Structure - Explanation:

* For Amount we used "Monto Original Contratado"
* For Maturirities we used "Fecha de Vencimiento" (note that there are some values)
* Other important dates are "Contract date", "Inscription Date" and "Days agreed for paying", we can add the "Contract date" or the "Inscription date" plus the "Days agreed for paying".
* For rates we used "Tasa Efectiva" but we can also use the "Tasa de interés", "Sobretasa", "Porcentaje Afectado" and "Tasa garantizada". 


```{r municipalities , echo=FALSE}
# Create a new data frame with rows containing "municipio"
registro_deuda_municipal_1 <- registro_deuda_1_[grepl("municipio", registro_deuda_1_$DEUDOR.U.OBLIGADO.2, ignore.case = TRUE), ]
# Create a new data frame with rows containing "municipal"

registro_deuda_municipal_2 <- registro_deuda_1_[grepl("municipal", registro_deuda_1_$DEUDOR.U.OBLIGADO.2, ignore.case = TRUE), ]
registro_deuda_municipal <- rbind(registro_deuda_municipal_1, registro_deuda_municipal_2)
registro_deuda_municipal <- registro_deuda_municipal[, c("MONTO.ORIGINAL.CONTRATADO.7/", "DEUDOR.U.OBLIGADO.2/", "FECHA.DE.VENCIMIENTO.27/", "TASA.EFECTIVA.13/")]
write.xlsx(registro_deuda_municipal, file = "registro_deuda_municipal.xlsx")
```


# Filter by states 
```{r municipalities , echo=FALSE}

# Create a new data frame with rows containing "Estado"
registro_deuda_estatal_1 <- registro_deuda_1_[grepl("Estado", registro_deuda_1_$DEUDOR.U.OBLIGADO.2, ignore.case = TRUE),]
# Create a new data frame with rows containing "Estatal"
registro_deuda_estatal_2 <- registro_deuda_1_[grepl("Estatal", registro_deuda_1_$DEUDOR.U.OBLIGADO.2, ignore.case = TRUE),]
registro_deuda_estatal <- rbind(registro_deuda_estatal_1, registro_deuda_estatal_2)
registro_deuda_estatal <- registro_deuda_estatal[, c("MONTO.ORIGINAL.CONTRATADO.7/", "DEUDOR.U.OBLIGADO.2/", "FECHA.DE.VENCIMIENTO.27/", "TASA.EFECTIVA.13/")]
write.xlsx(registro_deuda_estatal, file = "resgistro_deuda_estatal.xlsx")

```

